---
title: "Returns on Investment to Herbicides: Example of Spatial Economic Surplus Approach"
format: 
    html:
      code-fold: true
      code-tools: true
fig-dpi: 300
fig-width: 8.88
fig-align: center
fig-height: 5

self-contained: true
author: Maxwell Mkondiwa
editor: visual
toc: true
toc-location: left
number-sections: true
execute: 
  message: false
  warning: false
  echo: true
---

# Introduction

The conventional approach to valuing agricultural research is the economic surplus approach (Alston et al 1995). This approach is commonly applied to country wide research programs rather than disaggregated to district level. In this note, we demonstrate how to use causal machine learning heterogeneous treatment effects to make return on investment analyses that are sufficiently disaggregated.

# Steps in Return on Investment Economic Surplus Model

## Step 1: Baseline area, production, and yield

```{r, warning=FALSE}
library(rio)

APY_data <- import("Data_1997_23_Cleaned.xlsx", sheet = "All_data")

APY_data$Production_Tonnes <- as.numeric(APY_data$Production_Tonnes)

APY_data_wheat_2015_19 <- subset(APY_data, APY_data$Season == "Rabi" & APY_data$Crop == "Wheat" & APY_data$Year %in% c("2015-16", "2016-17", "2017-18", "2018-19", "2019-20"))

APY_data_wheat_2015_19$Season <- NULL
APY_data_wheat_2015_19$Crop <- NULL
APY_data_wheat_2015_19$Season <- NULL
library(data.table)
APY_data_wheat_2015_19 <- data.table(APY_data_wheat_2015_19)
APY_data_wheat_2015_19_ave <- APY_data_wheat_2015_19[, lapply(.SD, base::mean, na.rm = TRUE), by = .(Districts)]

APY_data_wheat_2015_19_ave <- APY_data_wheat_2015_19[, .(Area_Hectare = base::mean(Area_Hectare), Production_Tonnes = base::mean(Production_Tonnes), Yield_Tonnes_Hectare = base::mean(Yield_Tonnes_Hectare)), by = .(Districts)]

# Download all the data
library(reactable)
library(htmltools)
library(fontawesome)

htmltools::browsable(
    tagList(
        tags$button(
            tagList(fontawesome::fa("download"), "Download as CSV"),
            onclick = "Reactable.downloadDataCSV('APY_data_wheat_2015_19_ave', 'APY_data_wheat_2015_19_ave.csv')"
        ),
        reactable(
            APY_data_wheat_2015_19_ave,
            searchable = TRUE,
            defaultPageSize = 38,
            elementId = "APY_data_wheat_2015_19_ave"
        )
    )
)


# library(ggplot2)
# ggplot() +
#     geom_line(data = subset(APY_data, APY_data$Crop == "Wheat"), aes(x = Year, y = Area_Hectare, group = Districts, linetype = Districts, color = Districts), linewidth = 1.5) +
#     labs(x = "Year", y = "Area") +
#     theme_bw() 


# Having the baseline we need to create this from 2020 to 2030

library(tidyverse)
APY_data_wheat_2019_30 <- APY_data_wheat_2015_19_ave %>%
    mutate(year = list(2019:2030)) %>%
    separate_rows(year, sep = ",", convert = T)

# Delete Kishanganji due to lack of data
APY_data_wheat_2019_30 <- subset(APY_data_wheat_2019_30, !(APY_data_wheat_2019_30$Districts == "KISHANGANJ"))

```

## Step 2: Adoption data and projections

```{r, warning=FALSE}
# District level Cumulative Adoption -------------------------------------------
library(rio)
DistrictCumulativeAdoption=import("DistrictCumulativeAdoption.csv") 

# Manual
library(nlme)
DistrictCumulativeAdoption100=nlsList(cumulative_percent~100/(1 + exp(-(a + b*herbi_1st_use))),start=list(a = 1, b = 0),
                                      data=groupedData(cumulative_percent~herbi_1st_use|A.q103_district,DistrictCumulativeAdoption),na.action=na.omit)
summary(DistrictCumulativeAdoption100)
alphaDistrictCumulativeAdoption100 <- coef(DistrictCumulativeAdoption100) 
write.csv(alphaDistrictCumulativeAdoption100, file = "alphaDistrictCumulativeAdoption100.csv")

# SSLOGIS
SSlogDistrictCumulativeAdoption100=nlsList(cumulative_percent~SSlogis(herbi_1st_use, 100, xmid, scale),start=list( xmid=1992, scale=5),
                                           data=groupedData(cumulative_percent~herbi_1st_use|A.q103_district,DistrictCumulativeAdoption),na.action=na.omit,pool=FALSE)

summary(SSlogDistrictCumulativeAdoption100)

nlssummary=summary(SSlogDistrictCumulativeAdoption100)

xmid=nlssummary$coefficients[,,1]
colnames(xmid) <- paste("xmid", colnames(xmid), sep = "_")
scale=nlssummary$coefficients[,,2]
colnames(scale) <- paste("xmid", colnames(scale), sep = "_")

SSlogDistrictCumulativeAdoption100Results <-data.frame(coefficients(SSlogDistrictCumulativeAdoption100),xmid,scale)

library(broom)
library(tibble)
library(dplyr)
library(tidyr)
library(purrr)

SSlogDistrictCumulativeAdoption100Results$Slopes=1/SSlogDistrictCumulativeAdoption100Results$scale

SSlogDistrictCumulativeAdoption100Results$Intercept=-(SSlogDistrictCumulativeAdoption100Results$xmid/SSlogDistrictCumulativeAdoption100Results$scale)

SSlogDistrictCumulativeAdoption100Results$Year10percent=((-2.2-SSlogDistrictCumulativeAdoption100Results$Intercept)/SSlogDistrictCumulativeAdoption100Results$Slopes)
SSlogDistrictCumulativeAdoption100Results$Year90percent=((2.2-SSlogDistrictCumulativeAdoption100Results$Intercept)/SSlogDistrictCumulativeAdoption100Results$Slopes)
SSlogDistrictCumulativeAdoption100Results$Years10_90=SSlogDistrictCumulativeAdoption100Results$Year90percent-SSlogDistrictCumulativeAdoption100Results$Year10percent

write.csv(SSlogDistrictCumulativeAdoption100Results, file = "SSlogDistrictCumulativeAdoption100Results.csv")

herbi_1st_use <- with(DistrictCumulativeAdoption, seq(2000,2030, length.out = 31))
A.q103_district=levels(as.factor(DistrictCumulativeAdoption$A.q103_district))
herbi_1st_use_dist=expand.grid(herbi_1st_use=herbi_1st_use,A.q103_district=A.q103_district)
herbi_1st_use_dist$pred=predict(SSlogDistrictCumulativeAdoption100, herbi_1st_use_dist)
herbi_1st_use_dist_Data=merge(DistrictCumulativeAdoption,herbi_1st_use_dist,by=c("A.q103_district","herbi_1st_use"),all.y=TRUE)

write.csv(herbi_1st_use_dist_Data, file = "herbi_1st_use_dist_DataPredictionResults100.csv")


Herb_adoption=subset(herbi_1st_use_dist_Data, select=c("A.q103_district","herbi_1st_use","pred") )

names(Herb_adoption)[1:3]=c("Districts","year","Herb_adopt_perc")

write.csv(Herb_adoption, file = "Herb_adoption.csv")



# Plotting predicted herbicide adoption rates

ggplot(Herb_adoption,aes(y=Herb_adopt_perc,x=year,color=Districts)) + 
  geom_line()+
   theme_bw()+
  labs(y="Ädoption rate (% of farmers)")

# Subset the years 2019 to 2030 and three columns 


Herb_adoption_2019_30=subset(Herb_adoption,Herb_adoption$year%in%c(2019:2030))

ggplot(Herb_adoption_2019_30,aes(y=Herb_adopt_perc,x=year,color=Districts)) + 
  geom_line()

Herb_adoption_2019_30$Districts=toupper(Herb_adoption_2019_30$Districts)

APY_plus_adoption=merge(Herb_adoption_2019_30,APY_data_wheat_2019_30,by=c("Districts","year"))


APY_plus_adoption$Area_Hectare_Herb=(APY_plus_adoption$Herb_adopt_perc/100)*APY_plus_adoption$Area_Hectare



```

## Step 3: Supply, demand elasticities, and prices

```{r, warning=FALSE}
APY_plus_adoption$Supply_Elast=0.22 # Taken from Kumar et al 2016
APY_plus_adoption$Demand_Elast=0.340 # Taken from Kumar et al 2011

Prices=import("tabpricedist.csv")

Prices=subset(Prices,select=c("A.q103_district","mean"))

names(Prices)[1:2]=c("Districts","Prices")

Prices$Districts=toupper(Prices$Districts)

APY_plus_adoption=merge(APY_plus_adoption,Prices,by="Districts")


```

## Step 4: Yield and cost changes due to research

```{r, warning=FALSE}
library(rio)
Yield_changes=import("tau.hat_weeding_herb_predictions_dist.csv")

Yield_changes=subset(Yield_changes,select=c("A.q103_district","mean"))

names(Yield_changes)[1:2]=c("Districts","Yield_gain_t_ha")

Yield_changes$Districts=toupper(Yield_changes$Districts)

APY_plus_adoption=merge(APY_plus_adoption,Yield_changes,by="Districts")

# cost changes
APY_plus_adoption$Cost_changes=0

```

## Step 5: Research induced supply shift

```{r, warning=FALSE}

# K_shift_yld_compt

APY_plus_adoption$K_shift_yld_compt=APY_plus_adoption$Yield_gain_t_ha/APY_plus_adoption$Supply_Elast


# K_shift_cost_component
APY_plus_adoption$K_shift_cost_compt=APY_plus_adoption$Cost_changes/(1+(APY_plus_adoption$Yield_gain_t_ha/APY_plus_adoption$Yield_Tonnes_Hectare))

# K_shift
APY_plus_adoption$K_shift=APY_plus_adoption$K_shift_yld_compt-APY_plus_adoption$K_shift_cost_compt

APY_plus_adoption$K_shift_A=APY_plus_adoption$K_shift*APY_plus_adoption$Herb_adopt_perc*0.01

# Z_t=K_t e/e+eta

APY_plus_adoption$Z_t=(APY_plus_adoption$K_shift_A*APY_plus_adoption$Supply_Elast)/(APY_plus_adoption$Supply_Elast+APY_plus_adoption$Demand_Elast)


```

## Step 6: Compute producer surplus, consumer surplus and total surplus

For a small closed economy, the equations producer surplus, consumer surplus and total surplus.

Producer surplus

$$
\Delta PS_t = P_0Q_0 (K-Z)(1+0.5Z \eta)
$$

Consumer surplus $$
\Delta CS_t = P_0Q_0 Z(1+0.5Z \eta)
$$

Total surplus $$
\Delta TS_t =\Delta PS_t + \Delta CS_t 
$$

```{r, warning=FALSE}

# Producer surplus
#APY_plus_adoption$producer_surplus=APY_plus_adoption$Production_Tonnes*APY_plus_adoption$Prices*APY_plus_adoption$K_shift_A*(1-0.5*APY_plus_adoption$K_shift_A*APY_plus_adoption$Supply_Elast)

APY_plus_adoption$producer_surplus=APY_plus_adoption$Production_Tonnes*APY_plus_adoption$Prices*(APY_plus_adoption$K_shift_A-APY_plus_adoption$Z_t)*(1+0.5*APY_plus_adoption$Z_t*APY_plus_adoption$Demand_Elast)

APY_plus_adoption$producer_surplus_Rs_per_ha=(APY_plus_adoption$producer_surplus/APY_plus_adoption$Area_Hectare)*1000

# Consumer surplus
APY_plus_adoption$consumer_surplus=APY_plus_adoption$Production_Tonnes*APY_plus_adoption$Prices*APY_plus_adoption$Z_t*(1+0.5*APY_plus_adoption$Z_t*APY_plus_adoption$Demand_Elast)

# Total surplus
APY_plus_adoption$total_surplus=APY_plus_adoption$producer_surplus+APY_plus_adoption$consumer_surplus



```

### Small open economy producer surplus

For a small open economy in which the state's contribution cannot affect global prices, producer surplus can be computed as: $$
\Delta PS_t = P_0Q_0K_t(1-0.5K_t \epsilon)
$$

```{r}
APY_plus_adoption$producer_surplus_open_econ <- APY_plus_adoption$Production_Tonnes * APY_plus_adoption$Prices * (1 - 0.5 * APY_plus_adoption$K_shift_A * APY_plus_adoption$Supply_Elast)

APY_plus_adoption$producer_surplus_open_econ_Rs_per_ha <- (APY_plus_adoption$producer_surplus_open_econ / APY_plus_adoption$Area_Hectare) * 1000

```

## Step 7: Cost of research

```{r, warning=FALSE}
APY_plus_adoption$Cost_of_research=0

```

## Step 8: Compute economic indicators

```{r, warning=FALSE}
# Discount rate
APY_plus_adoption$discount_rate <- 0.2

# time
APY_plus_adoption$time <- APY_plus_adoption$year - 2019

# cashflows
APY_plus_adoption$net_producer_surplus <- APY_plus_adoption$producer_surplus - APY_plus_adoption$Cost_of_research

APY_plus_adoption$net_producer_surplus_open_econ <- APY_plus_adoption$producer_surplus_open_econ - APY_plus_adoption$Cost_of_research

APY_plus_adoption$net_consumer_surplus <- APY_plus_adoption$consumer_surplus - APY_plus_adoption$Cost_of_research

APY_plus_adoption$net_total_surplus <- APY_plus_adoption$total_surplus - APY_plus_adoption$Cost_of_research

# Calculate the Present Value of Each Cash Flow
APY_plus_adoption$Producer_present_value <- APY_plus_adoption$net_producer_surplus / ((1 + APY_plus_adoption$discount_rate)^APY_plus_adoption$time)

APY_plus_adoption$Producer_present_value_open_econ <- APY_plus_adoption$net_producer_surplus_open_econ / ((1 + APY_plus_adoption$discount_rate)^APY_plus_adoption$time)

APY_plus_adoption$Consumer_present_value <- APY_plus_adoption$net_consumer_surplus / ((1 + APY_plus_adoption$discount_rate)^APY_plus_adoption$time)

APY_plus_adoption$Total_present_value <- APY_plus_adoption$net_total_surplus / ((1 + APY_plus_adoption$discount_rate)^APY_plus_adoption$time)


# Sum all the Present Values
library(data.table)
APY_plus_adoption <- data.table(APY_plus_adoption)

APY_plus_adoption_indic <- APY_plus_adoption[, .(
    Producer_net_present_value_sum = base::sum(Producer_present_value, na.rm = TRUE),
    Producer_present_value_open_econ_sum = base::sum(Producer_present_value_open_econ, na.rm = TRUE),
    Consumer_net_present_value_sum = base::sum(Consumer_present_value, na.rm = TRUE),
    Total_net_present_value_sum = base::sum(Total_present_value, na.rm = TRUE),
    Wheat_area_mean = base::mean(Area_Hectare, na.rm = TRUE),
    Area_Hectare_Herb_mean = base::mean(Area_Hectare_Herb, na.rm = TRUE),
    Production_Tonnes_mean = base::mean(Production_Tonnes, na.rm = TRUE),
    Yield_Tonnes_Hectare_mean = base::mean(Yield_Tonnes_Hectare, na.rm = TRUE)
), by = .(Districts)]

# Producer surplus small open economy
APY_plus_adoption_indic$Producer_present_value_open_econ_sum_annual <- APY_plus_adoption_indic$Producer_present_value_open_econ_sum / 11
sum(APY_plus_adoption_indic$Producer_present_value_open_econ_sum_annual)
summary(APY_plus_adoption_indic$Producer_present_value_open_econ_sum_annual)

APY_plus_adoption_indic$Producer_present_value_open_econ_sum_annual_Rs_ha <- (APY_plus_adoption_indic$Producer_present_value_open_econ_sum_annual / APY_plus_adoption_indic$Wheat_area_mean) * 1000

summary(APY_plus_adoption_indic$Producer_present_value_open_econ_sum_annual_Rs_ha)

# Producer surplus
APY_plus_adoption_indic$Producer_net_present_value_sum_annual <- APY_plus_adoption_indic$Producer_net_present_value_sum / 11

sum(APY_plus_adoption_indic$Producer_net_present_value_sum_annual)
summary(APY_plus_adoption_indic$Producer_net_present_value_sum_annual)

APY_plus_adoption_indic$Producer_net_present_value_sum_annual_Rs_ha <- (APY_plus_adoption_indic$Producer_net_present_value_sum_annual / APY_plus_adoption_indic$Wheat_area_mean) * 1000

summary(APY_plus_adoption_indic$Producer_net_present_value_sum_annual_Rs_ha)

# Consumer surplus
APY_plus_adoption_indic$Consumer_net_present_value_sum_annual <- APY_plus_adoption_indic$Consumer_net_present_value_sum / 11

sum(APY_plus_adoption_indic$Consumer_net_present_value_sum_annual)
summary(APY_plus_adoption_indic$Consumer_net_present_value_sum_annual)

APY_plus_adoption_indic$Consumer_net_present_value_sum_annual_Rs_ha <- (APY_plus_adoption_indic$Consumer_net_present_value_sum_annual / APY_plus_adoption_indic$Wheat_area_mean) * 1000

summary(APY_plus_adoption_indic$Consumer_net_present_value_sum_annual_Rs_ha)


# Total surplus
APY_plus_adoption_indic$Total_net_present_value_sum_annual <- APY_plus_adoption_indic$Total_net_present_value_sum / 11

sum(APY_plus_adoption_indic$Total_net_present_value_sum_annual)
summary(APY_plus_adoption_indic$Total_net_present_value_sum_annual)

APY_plus_adoption_indic$Total_net_present_value_sum_annual_Rs_ha <- (APY_plus_adoption_indic$Total_net_present_value_sum_annual / APY_plus_adoption_indic$Wheat_area_mean) * 1000

summary(APY_plus_adoption_indic$Total_net_present_value_sum_annual_Rs_ha)

# Benefit-cost ratio
# APY_plus_adoption$BCR=APY_plus_adoption$producer_surplus/APY_plus_adoption$Cost_of_research

# Internal Rate of Return (IRR)

# IRR(cf0,cf,times,plot=FALSE)
# MIRR=

# irr1 <- project1_cf %>%
#   select(cf) %>%
#   .[[1]] %>%
#   irr()

# Modified Internal Rate of Return (MIRR)



```

# Spatial visualization of the economic surpluses

```{r}
library(geodata)

India <- gadm(country = "IND", level = 2, path = "shp")
plot(India)

India_aoi <- subset(India, India$NAME_1 == "Bihar")

plot(India_aoi)

plot(India_aoi, add = TRUE)

library(sf)

India_aoi_sf <- st_as_sf(India_aoi)
library(mapview)

mapview(India_aoi_sf)

India_aoi_sf$Districts <- toupper(India_aoi_sf$NAME_2)

APY_plus_adoption_indic_sf <- merge(India_aoi_sf, APY_plus_adoption_indic, by = "Districts")

# Average wheat area
# Using tmap
library(tmap)
tmap_mode("plot")

Wheat_area_sf_tmap <- tm_shape(APY_plus_adoption_indic_sf) +
    tm_borders(alpha = 0.5, col = "white") +
    tm_polygons(col = "Wheat_area_mean", palette = "viridis", scale = 2.5, title = "Wheat area (ha)")
Wheat_area_sf_tmap

tmap_save(Wheat_area_sf_tmap, "figures/Wheat_area_sf_tmap.png", dpi = 300, width = 4.88, height = 3.16)

# Average wheat yields
tmap_mode("plot")

Wheat_yield_sf_tmap <- tm_shape(APY_plus_adoption_indic_sf) +
    tm_borders(alpha = 0.5, col = "white") +
    tm_polygons(col = "Yield_Tonnes_Hectare_mean", palette = "viridis", scale = 2.5, title = "Wheat yields (t/ha)")
Wheat_yield_sf_tmap

tmap_save(Wheat_yield_sf_tmap, "figures/Wheat_yield_sf_tmap.png", dpi = 300, width = 4.88, height = 3.16)


# Average wheat production
tmap_mode("plot")

Wheat_production_sf_tmap <- tm_shape(APY_plus_adoption_indic_sf) +
    tm_borders(alpha = 0.5, col = "white") +
    tm_polygons(col = "Production_Tonnes_mean", palette = "viridis", scale = 2.5, title = "Wheat production (t)")
Wheat_production_sf_tmap

tmap_save(Wheat_production_sf_tmap, "figures/Wheat_production_sf_tmap.png", dpi = 300, width = 4.88, height = 3.16)



# Producer surplus

mapview(APY_plus_adoption_indic_sf, zcol = "Producer_net_present_value_sum_annual", layer.name = "Producer surplus (INR 1000)")

# Using tmap
library(tmap)
tmap_mode("plot")

prod_surplus_changes_sf_tmap <- tm_shape(APY_plus_adoption_indic_sf) +
    tm_borders(alpha = 0.5, col = "white") +
    tm_polygons(col = "Producer_net_present_value_sum_annual", palette = "viridis", scale = 2.5, title = "Producer surplus (INR 1000)")
prod_surplus_changes_sf_tmap

tmap_save(prod_surplus_changes_sf_tmap, "figures/prod_surplus_changes_sf_tmap.png", dpi = 300, width = 3.88, height = 3.16)

# Small open economy
library(tmap)
tmap_mode("plot")

prod_surplus_changes_open_econ_sf_tmap <- tm_shape(APY_plus_adoption_indic_sf) +
    tm_borders(alpha = 0.5, col = "white") +
    tm_polygons(col = "Producer_present_value_open_econ_sum_annual", palette = "viridis", scale = 2.5, title = "Small open economy PS (INR 1000)")
prod_surplus_changes_open_econ_sf_tmap

tmap_save(prod_surplus_changes_open_econ_sf_tmap, "figures/prod_surplus_changes_open_econ_sf_tmap.png", dpi = 300, width = 3.88, height = 3.16)



# Producer surplus per ha
# Using tmap
library(tmap)
tmap_mode("plot")

prod_surplus_changes_perha_sf_tmap <- tm_shape(APY_plus_adoption_indic_sf) +
    tm_borders(alpha = 0.5, col = "white") +
    tm_polygons(col = "Producer_net_present_value_sum_annual_Rs_ha", palette = "viridis", scale = 2.5, title = "Producer surplus per ha")
prod_surplus_changes_perha_sf_tmap


tmap_save(prod_surplus_changes_perha_sf_tmap, "figures/prod_surplus_changes_perha_sf_tmap.png", dpi = 300, width = 3.88, height = 3.16)

## Small open economy
library(tmap)
tmap_mode("plot")

prod_surplus_changes_open_econ_perha_sf_tmap <- tm_shape(APY_plus_adoption_indic_sf) +
    tm_borders(alpha = 0.5, col = "white") +
    tm_polygons(col = "Producer_present_value_open_econ_sum_annual_Rs_ha", palette = "viridis", scale = 2.5, title = "Small open economy PS per ha")
prod_surplus_changes_open_econ_perha_sf_tmap


tmap_save(prod_surplus_changes_open_econ_perha_sf_tmap, "figures/prod_surplus_changes_open_econ_perha_sf_tmap.png", dpi = 300, width = 3.88, height = 3.16)



mapview(APY_plus_adoption_indic_sf, zcol = "Consumer_net_present_value_sum_annual", layer.name = "Consumer surplus (INR 1000)")

mapview(APY_plus_adoption_indic_sf, zcol = "Total_net_present_value_sum_annual", layer.name = "Total economic surplus (INR 1000)")


library(reactable)
library(htmltools)
library(fontawesome)

htmltools::browsable(
    tagList(
        tags$button(
            tagList(fontawesome::fa("download"), "Download as CSV"),
            onclick = "Reactable.downloadDataCSV('APY_plus_adoption_indic_sf', 'APY_plus_adoption_indic_sf.csv')"
        ),
        reactable(
            APY_plus_adoption_indic_sf,
            searchable = TRUE,
            defaultPageSize = 38,
            elementId = "APY_plus_adoption_indic_sf"
        )
    )
)

# Yield changes
Yield_changes <- subset(Yield_changes, !(Yield_changes$Districts == "KISHANGANJ"))

library(mapview)
Yield_changes_sf <- merge(India_aoi_sf, Yield_changes, by = "Districts")

mapview(Yield_changes_sf, zcol = "Yield_gain_t_ha", layer.name = "Yield gain to herbicides (tons per ha)")

# Using tmap
library(tmap)
tmap_mode("plot")

Yield_changes_sf_tmap <- tm_shape(Yield_changes_sf) +
    tm_borders(alpha = 0.5, col = "white") +
    tm_polygons(col = "Yield_gain_t_ha", palette = "viridis", scale = 2.5, title = "Yield gain to herbicides (tons per ha)")
Yield_changes_sf_tmap

tmap_save(Yield_changes_sf_tmap, "figures/Yield_changes_sf_tmap.png", dpi = 300, width = 3.88, height = 3.16)



library(reactable)
library(htmltools)
library(fontawesome)

htmltools::browsable(
    tagList(
        tags$button(
            tagList(fontawesome::fa("download"), "Download as CSV"),
            onclick = "Reactable.downloadDataCSV('Yield_changes_sf', 'Yield_changes_sf.csv')"
        ),
        reactable(
            Yield_changes_sf,
            searchable = TRUE,
            defaultPageSize = 38,
            elementId = "Yield_changes_sf"
        )
    )
)

```

# Conclusion

The notebook has demonstrated the workflow for calculating spatially disaggregated economic surplus measures that can be used to target and prioritize agricultural interventions.

# References

Alston, J.M., Norton, G.W., and Pardey, P.G. 1995. "Science under scarcity: Principles and practice for agricultural research evaluation and priority setting." CAB International. Wallingford, UK.
